method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added loop

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())

@@

>>>>

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double(), trigger_view = double(), trigger_reg = double())

@@

# loop to correct block indicator

for (i in 1:nrow(data_ER)) {

  if (data_ER$trigger_view[i] == 21 & is.na(data_ER$trigger_reg[i])) {

    data_ER$block[i] = "view_neu"

  } else if (data_ER$trigger_view[i] == 22 & is.na(data_ER$trigger_reg[i])) {

    data_ER$block[i] = "view_neg"

  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 23) {

    data_ER$block[i] = "distraction"

  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 24) {

    data_ER$block[i] = "distancing"

  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 25) {

    data_ER$block[i] = "suppression"

  } else if (is.na(data_ER$trigger_view[i]) & is.na(data_ER$trigger_reg[i])) {

    data_ER$block[i] = "choice"
  }
}
